Awareness and Russellian Epistemology

### 2011-01-30 awareness.tex
Changed how awareness sets are typeset

Aside from \textbf{CSQ$_\vdash$}, we will be concerned with the
following new property

\begin{definition}\label{snd1}
  \begin{descriptiondash}
    \item[SND] If $\mathbbm{M}, w \vDash \circlearrowleft \text{ then }
    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
  \end{descriptiondash}
\end{definition}

The logic for \textbf{CSQ$_\vdash$} and \textbf{SND} differs from the
logic given in \S\ref{awarenesslogic0} by a single axiom:

@@

\begin{theorem}
  \label{completeness1}Assuming an infinite store of proposition letters
  $\Phi$, the awareness logic presented is sound and weakly complete for
  awareness models making true \tmtextbf{CSQ}$_{\vdash'}$ and
  \tmtextbf{SND} for a suitable logic $\vdash'$.
\end{theorem}
\begin{proof}
The proof proceeds exactly as the proof of Theorem
\ref{completeness0}; the only difference is that the canonical model
and modified model make true \textbf{SND} instead of being reflexive.
\end{proof}

>>>>

Aside from $\textup{\textbf{CSQ}}_\vdash$, we will be concerned with
the following new property

\begin{definition}\label{snd1}
  \begin{descriptiondash}
    \item[SND] If $\mathbbm{M}, w \vDash \circlearrowleft \text{ then }
    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}(w)$
  \end{descriptiondash}
\end{definition}

The logic for  $\textup{\textbf{CSQ}}_\vdash$ and \textbf{SND} differs from the
logic given in \S\ref{awarenesslogic0} by a single axiom:

@@

\begin{theorem}
  \label{completeness1}Assuming an infinite store of proposition letters
  $\Phi$, the awareness logic presented in Table \ref{logic1} is sound and weakly complete for
  $\PP$-awareness models making true \tmtextbf{CSQ}$_{\vdash'}$ for a
  suitable logic $\vdash'$ as well as
  \tmtextbf{SND}.
\end{theorem}
\begin{proof}
The proof proceeds exactly as the proof of Theorem
\ref{completeness0}; the only difference is that the canonical model
and modified model make true \textbf{SND} instead of being reflexive.
\end{proof}
